% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Dmitrii Banshchikov}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://github.com/ubique/cv/cv.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {software engineering},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\usepackage{relsize}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  {Software Engineer } \\
\end{minipage}
\begin{minipage}{0.45\linewidth}
\end{minipage}


\section*{Education}

\begin{itemize}
  \item B.E.T. with the major in Optical Engineering, Saint Petersburg State University of Information Technologies, Mechanics and Optics, 2010.
\end{itemize}


\section*{Employment}

\begin{itemize}
\item PeterHost, System Administrator, 2009--2011.
\item Yandex, Junior System Administrator, 2011--2012.
\item Hosting Community, System Administrator, 2012--2013.
\item Doctor Web, Software Engineer, 2013--2017.
\item VK, Software Engineer, 2017--2018.
\item VK, Senior Software Engineer, 2018--2019.
\item Facebook, Production Engineer, 2019--2020.
\item Telegram, Software Engineer, 2020--till present.
\end{itemize}


\section*{Area of interest}

\subsection*{Experience}
\begin{itemize}
\item The main focus is networking and system software and its performance.
\item Effective Vector Crypto Primitives.
\item Linux Kernel Patchsets.
\item Linux Kernel Module Development.
\end{itemize}

\subsection*{Conferences}

\begin{itemize}
\item PowerDNS at the scale of hosting provider, 2009, {\it HighLoad++}.
\item Shared Libraries without External Dependencies, 2018, {\it C++ Russia}.
\item BPF based firewall, 2021, {\it Linux Plumbers Conference}.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
